\section{Search completeness and independent checks}
\label{app:search}

This appendix makes the finite proof contract explicit.  Let $M=2^{24}-1$
be the full chamber mask and let $N(U)$ denote the distinct left translates
of $U$.

\subsection{Connected-mask scan}

For each nonzero integer $m\le M$, breadth-first search in the induced
right-Cayley graph decides connectivity.  Each connected mask is emitted
once in numeric order.  The observed stream has $1{,}210{,}648$ entries and a
pinned stream hash.  The eligibility predicate is
\[
 24\equiv0\pmod{|U|}.
\]
Canonicalisation applies all $24$ precomputed left-action bit permutations
and keeps the minimum.  The idempotence checks
$\can_L(\can_L(U))=\can_L(U)$ and
$\can_L(gU)=\can_L(U)$ are run throughout the candidate space.

\subsection{Exact-cover decision}

The decision search memoises remaining masks.  If $c$ is the least uncovered
chamber, every completion contains one and only one member of $N(U)$ that
contains $c$.  This proves the recursion of \cref{alg:exact-cover} complete.
For the all-cover census, memoisation is removed from the output layer and
the recursion emits every terminal unordered family.  A separate
combination enumerator tests every $24/|U|$-subset of $N(U)$; its sorted cover
stream agrees exactly with the recursive stream on all $82$ positive rows.

\subsection{Orbit checks}

Tile, cover, and selector canonical keys are computed by explicit minimisation
over all $24$ group elements.  Stabiliser sizes satisfy orbit--stabiliser in
every record.  Cover and selector orbit totals are independently checked by
Burnside averaging.  All $30$ subgroups of $S_4$ are generated from closure,
not read from a hand-written list; their type histogram is checked against
the subgroup inventory in the certificate.

\subsection{Geometric checks}

Boundary vertices and planes are rational in the standard simplex model.
For each of the $2{,}874$ eligible canonical candidates, the gate extracts
every boundary triangle, forms primitive normal lines, verifies that no mesh
edge supports a rank-three nonvertex stratum, and checks that $C_3(U)$ has
affine rank three.  This remains valid for the $1{,}809$ candidates whose raw
boundary triangulations have nonmanifold edge incidence, by
\cref{lem:corner-strata}.

Covariance under all coordinate permutations is proved at the carrier level
rather than sampled mask by mask.  Exact audits of chamber bijections,
chamber tetrahedra, facet occurrences, equality of facet keys, and primitive
normal lines show that boundary extraction and normal rank commute with
$\Phi_g$ for every one of the $2^{24}$ masks.  This single finite proof
implies the $68{,}976$ candidate-action cases used in the canonical
reduction.

Complete point-set isometries of the canonical rank-three corner loci are
then enumerated by both distance-graph backtracking and affine-Gram
reconstruction.  The two lanes exhaust the same $290$ class pairs, agree on
all $617$ class-level maps, and find neither a cross-class isometry nor a
non-$S_4$ map.  Recorded coordinate transporters derive the corresponding
$228{,}599$ maps on the original candidate pairs.  On the selected $82$
atlas rows, candidate maps are additionally filtered against exact chamber
masks to recover self-isometry groups and chirality.  Synthetic
perturbations, coplanar subdivisions, a corner-set symmetry that fails the
mask filter, and a non-$S_4$ synthetic isometry exercise the rejection paths.

The tests establish completeness inside the declared finite universe.  They
do not convert the universe into a statement about arbitrary dissections.
