The barycentric $A_3$ dissection of a regular tetrahedron consists of $24$
orthoscheme chambers naturally indexed by $S_4$.  Earlier work classified the
$15$ connected convex Coxeter-pure tiling orbits, reported an exhaustive audit
count of $82$ connected nonconvex left-translate tiling orbits, and posed the
classification of nonconvex congruent tilers as an open problem.  We close
that problem within the fixed Coxeter-pure carrier.  On all $2{,}874$ eligible
connected chamber-union orbits, an exact rank-three corner-locus audit proves
that free Euclidean congruence is precisely left $S_4$ equivalence.  Hence
congruent Coxeter-pure covers are exactly left-translate covers.  We then
construct the complete canonical atlas behind the earlier count and determine
its cover, contact, and symmetry structure.

The $82$ nonconvex orbits have chamber sizes $6,8,12$, with multiplicities
$14,18,50$.  The element-labelled right Patterson function
$a_U(h)=\abs{U\cap Uh}$ separates all atlas rows, whereas three natural
compressions yield only $20$, $33$, and $32$ classes.  We enumerate $786$
exact covers, $86$ cover orbits, $1{,}148$ multiplier selectors, and $102$
selector orbits; every selector-independent carrier is a typed double coset.
Rank-coloured contact complexes distinguish information invisible to their
rank marginals and produce two certified local-to-global obstruction pairs.
The atlas has $82$ full and $159$ oriented tile-congruence classes; its $86$
partition classes split into $151$ oriented classes, all are tile-transitive
inside the tetrahedron, and $69$ are rotation-tile-transitive.  Every result is
an exact finite statement for the fixed $A_3$ carrier: every partition member
is a union of its chambers.  The previously published count $15+82$ is prior
art and a replay target, not a novelty claim.
