\section{Introduction}\label{sec:introduction}

\subsection{From the convex catalogue to the nonconvex atlas}

The barycentric subdivision of a regular tetrahedron is simultaneously a
geometric dissection into $24$ congruent orthoschemes and the spherical
Coxeter complex of type $A_3$ coned to the barycentre.  This coincidence
makes a finite classification possible: unions of chambers become subsets of
$S_4$, adjacency is a Cayley-graph relation, and tetrahedral relabelling is
left multiplication.  The finite model is small enough for exhaustive
enumeration but large enough for nonconvexity, multiple exact covers,
chirality, and contact phenomena that do not occur in the convex catalogue.

The convex theory was developed in \cite{BabanskyyT2}.  There, connected
convex chamber unions were identified with poset cones, and the tiling pieces
were classified by the $15$ series--parallel poset types on four elements.
The same project reported an independent exhaustive count
\[
  97=15+82
\]
of connected left-translate tiling orbits, with $82$ nonconvex rows, and
posed the classification of connected nonconvex chamber unions that tile by
congruent copies as an open problem.  The numerical split is therefore
self-prior-art.  The purpose of this paper is to close the congruence gap
left by that audit and replace the bare count by a canonical, structurally
complete, and independently replayable atlas.

Four questions drive the construction.
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item Does free Euclidean congruence enlarge a left $S_4$ orbit anywhere in
the complete eligible chamber-union carrier?
\item Can the $82$ rows be separated by an intrinsic invariant that respects
the locked tetrahedral action?
\item How many inequivalent exact covers does each tile admit, and what is the
algebraic structure of its multiplier choices?
\item Which contact and symmetry data survive after local compression, and
where do local equivalences fail to assemble globally?
\end{enumerate}

The answers use four different layers.  An all-candidate rank-three
corner-locus theorem identifies free congruence with the locked left action.
The labelled right Patterson function separates tile orbits.  Exhaustive
exact-cover and multiplier enumeration describes all partitions inside the
finite carrier.  Exact rank-coloured barycentric intersections then recover
contact, handedness, and finite-container transitivity.

\subsection{Main results}

The main theorem packages the numerical statements; precise definitions and
stronger typed formulations appear in later sections.

\begin{theorem}[Nonconvex $A_3$ chamber atlas: overview]
\label{thm:overview}
In the fixed $24$-chamber $A_3$ dissection of the regular tetrahedron, under
the action and equivalences of \cref{sec:model}, the following hold.
\begin{enumerate}[label=(\alph*),leftmargin=2.2em]
\item There are exactly $82$ free-congruence classes of connected
halfspace-nonconvex pieces that tile by congruent Coxeter-pure copies.  Every
such copy is a left $S_4$ translate.  Their chamber sizes are $6,8,12$, with
multiplicities $14,18,50$.
\item The full element-labelled right Patterson vector separates the $82$
orbits.  Conjugacy-class sums, within-class coordinate multisets, and the
fully unlabelled coordinate multiset yield respectively $20,33,32$ classes.
\item The $82$ tiles admit $786$ exact covers in $86$ global-left cover
orbits.  Their $1{,}148$ multiplier selectors form $102$ selector orbits,
with the exact taxonomy $90+2+10$ described in \cref{sec:covers}.
\item Canonical representatives of the $86$ cover orbits have $212$
within-cover contact edges and $82$ edgewise signatures.  Two pairs are
edgewise equivalent but not globally aligned.
\item The atlas has $82$ full Euclidean and $159$ orientation-preserving tile
classes, split into $77$ chiral and $5$ achiral full classes.  The $86$
partition classes split into $151$ oriented classes; all $86$ are
finite-container tile-transitive and $69$ are rotation-tile-transitive.
\end{enumerate}
\end{theorem}

Part~(a) combines the left-exact-cover census with the independent
all-candidate rigidity theorem \cref{thm:global-rigidity}.  The latter ranges
over all $2{,}874$ eligible connected chamber-union orbits, not merely the
$82$ positive rows, and shows that every congruent Coxeter-pure cover is
already a left-translate cover; see \cref{cor:congruent-atlas}.  Here
\emph{Coxeter-pure} means that every partition member remains a union of the
fixed $A_3$ chambers.

The result in part~(b) is deliberately bounded.  Patterson functions and
homometry are classical \cite{MandereauEtAl2011,RosenblattSeymour1982,
GenuysPopoff2018}.  We prove injectivity only on the displayed $82$-row
family, not for arbitrary subsets of a finite group.  Likewise, the contact
and symmetry statements are about a finite tetrahedral container, not a
periodic monohedral tiling of Euclidean space.

\subsection{Why the labels and types matter}

Several superficially similar objects must remain distinct.  A tile orbit is
not a cover orbit; a cover is not a multiplier selector; the stabiliser of a
tile is not the stabiliser of a cover; an edgewise family of contact
equivalences is not one globally coherent equivalence.  Losing these types
creates false uniqueness and false local-to-global statements.  The paper
therefore fixes all actions, quotient relations, and quantifier orders before
stating the enumerative results.

The same discipline explains the Patterson theorem.  Left multiplication
fixes every labelled coordinate, while right multiplication conjugates the
coordinate labels.  The values alone do not suffice: all three natural label
compressions collide.  Thus the nonabelian labelling is not decorative data;
it is the separating information on this carrier.

\subsection{Logical status and organisation}

The three-way equivalence between halfspace, chamber-geodesic, and Euclidean
convexity for connected $A_3$ chamber unions is imported from
\cite{BabanskyyT2}.  All enumerations, Patterson identities, exact-cover
classifications, contact comparisons, and ambient congruence calculations in
this paper use exact integer or rational arithmetic.  The companion package
fully reconstructs the connected and eligible census, the global congruence
gate, and the congruent-copy exact-cover closure.  The Patterson, cover,
selector, contact, boundary, and ambient-symmetry layers are distributed as
exact parent-pinned snapshots with record hashes and public structural
recheckers; their production builders remain internal.  In particular, the
congruence statement is deduced only after the complete eligible carrier has
passed both exact isometry lanes.  A machine certificate supports a finite
proof; its stated replay level is part of the claim boundary and does not
enlarge the theorem's scope.

\Cref{sec:model} fixes the geometric and group-theoretic model.
\Cref{sec:finite-reduction} proves the finite reduction and constructs the
atlas.  \Cref{sec:patterson} develops the separating invariant.
\Cref{sec:covers,sec:contacts} classify covers, selectors, and contact
complexes.  \Cref{sec:ambient} treats congruence and transitivity, and
\cref{sec:boundary} records a presentation-sensitivity result.  The final
sections delimit prior art and give the replay contract.  The appendices
provide the search proof, the complete $82$-row catalogue, and a
theorem-to-certificate crosswalk.
