\section{The element-labelled Patterson separator}
\label{sec:patterson}

\subsection{Right differences in the group ring}

For $U\subseteq G$ write $X_U=\sum_{u\in U}u$ in the integral group ring
$\mathbb Z[G]$, and let $X_U^{(-1)}=\sum_{u\in U}u^{-1}$.  The coefficient of
$h$ in $X_U^{(-1)}X_U$ is
\[
 a_U(h)=|U\cap Uh|=\#\{(u,v)\in U^2:u^{-1}v=h\}.
\]
This is the right interval content, or right Patterson function, in counting
measure.  The left/right distinction is essential in a nonabelian group
\cite{MandereauEtAl2011,GenuysPopoff2018}.

\begin{lemma}[Patterson identities]\label[lemma]{lem:patterson-identities}
For $U\subseteq G$ and $g,h\in G$,
\begin{align*}
a_U(e)&=|U|,&
\sum_{h\in G}a_U(h)&=|U|^2,&
a_U(h)&=a_U(h^{-1}),\\
a_{gU}(h)&=a_U(h),&
a_{Ug}(h)&=a_U(ghg^{-1}),&
a_{G\setminus U}(h)&=|G|-2|U|+a_U(h).
\end{align*}
\end{lemma}
\begin{proof}
The first identity counts diagonal pairs, the second all ordered pairs in
$U^2$, and inversion exchanges $(u,v)$ with $(v,u)$.  In a left translate,
$(gu)^{-1}(gv)=u^{-1}v$.  In a right translate,
$(ug)^{-1}(vg)=g^{-1}u^{-1}vg$, which gives the displayed conjugation after
renaming the argument.  Finally, expand the two complement indicators in
$\sum_x(1-1_U(x))(1-1_U(xh^{-1}))$.
\end{proof}

The formula for right translation explains why coordinate labels cannot be
discarded casually.  Left translation fixes the vector pointwise; right
translation permutes it through inner automorphisms.

\subsection{Three controlled compressions}

Let $C_1,\ldots,C_5$ be the conjugacy classes of $S_4$.  We compare four
fingerprints:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item the full labelled vector $(a_U(h))_{h\in G}$ in the fixed word order;
\item the five conjugacy-class sums
$\bigl(\sum_{h\in C_i}a_U(h)\bigr)_i$;
\item the ordered five-tuple of multisets
$\bigl(\{a_U(h):h\in C_i\}_{\mathrm{multi}}\bigr)_i$;
\item the single unlabelled multiset
$\{a_U(h):h\in G\}_{\mathrm{multi}}$.
\end{enumerate}
These are distinct declared quotients of the data, not interchangeable
notions of Patterson equivalence.

\begin{theorem}[Labelled Patterson separation]\label{thm:patterson}
On the $82$ rows of \cref{thm:left-atlas}, the full element-labelled right
Patterson vector is injective.  The four fingerprints above yield
\[
\begin{array}{c|cccc}
&\text{full labelled}&\text{class sums}&\text{class multisets}&
\text{unlabelled}\\ \hline
\#\text{ classes}&82&20&33&32.
\end{array}
\]
The $24$ stored coordinates occupy $17$ orbits under inversion.
\end{theorem}
\begin{proof}
For every row the $24$ coefficients are computed by exact integer
intersection.  Equality grouping gives $82$ full vectors and, after applying
each displayed quotient, $20,33,32$ classes.  The identities of
\cref{lem:patterson-identities} are checked in all $82\cdot24=1{,}968$
left-translation cases.  Inversion fixes the identity, the six
transpositions, and the three double transpositions; the other $14$ elements
form seven inverse pairs.  Thus there are $10+7=17$ inversion positions.
\end{proof}

\begin{remark}[Scope]
The theorem is a collision-free certificate on one finite family.  It is not
a phase-retrieval theorem and does not assert that second-order
autocorrelation separates arbitrary subsets of $S_4$, still less arbitrary
finite groups.  Higher-order invariants can be complete under hypotheses
where second-order data are not \cite{Kakarala2012,RadcliffeScott2007}.
\end{remark}

\subsection{The half-size complement ambiguity}

For $|U|=|G|/2$, \cref{lem:patterson-identities} gives
$a_{G\setminus U}=a_U$.  This universal ambiguity does not produce a second
atlas row in the $K12$ family.

\begin{lemma}[Complement absorption]\label[lemma]{lem:complement}
For every one of the $50$ atlas rows with $|U|=12$, the complement
$G\setminus U$ belongs to the same left tile orbit as $U$.
\end{lemma}
\begin{proof}
Every such row has a two-piece left-translate cover
$G=g_1U\sqcup g_2U$.  Multiplication by $g_1^{-1}$ gives
$G=U\sqcup gU$, where $g=g_1^{-1}g_2$.  Hence $G\setminus U=gU$.
The certificate additionally checks the relation directly for all $50$
canonical masks.
\end{proof}

The convex catalogue admits a compact separating contact vector
\cite{BabanskyyT2}.  In the nonconvex atlas, the full right-difference labels
play the parallel role.  The compression profile $82/20/33/32$ quantifies
exactly how much separation is lost when those labels are forgotten.
