\section{All covers and multiplier selectors}\label{sec:covers}

\subsection{Cover orbits and selector fibres}

Fix an atlas row $U$ and an exact cover $\C$.  Besides the tile stabiliser
$H_U$, two further objects are needed:
\[
 K_\C=\Stab_L(\C)=\{g\in G:g\C=\C\}
\]
and the selector-independent lift
\[
 B_\C=\{g\in G:gU\in\C\}.
\]
The set of selectors realising this cover is
\[
 R_U(\C)=\{A\subseteq G:\{aU:a\in A\}=\C\}.
\]
Each piece $gU$ has multiplier fibre $gH_U$, so a selector chooses one
element from each such right coset.  In particular, selectors encode more
than the underlying geometric cover.

\begin{lemma}[Selector-independent carrier]\label[lemma]{lem:selector-carrier}
For every $A\in R_U(\C)$,
\[
 B_\C=AH_U,
 \qquad K_\C=\Stab_L(B_\C).
\]
Thus $B_\C$ depends on $U$ and $\C$, but not on the chosen section $A$.
\end{lemma}
\begin{proof}
The multipliers producing the piece $aU$ are precisely the elements of the
right coset $aH_U$.  Taking the union over $a\in A$ gives $B_\C=AH_U$.
A group element stabilises the cover if and only if it stabilises its full
preimage under the quotient map $g\mapsto gU$, proving the second identity.
\end{proof}

For each row we enumerate every exact cover by two algorithms: the recursive
search of \cref{alg:exact-cover} and direct combination testing inside the
left tile orbit.  Covers are canonicalised by
\[
 \can_G(\C)=
 \min_{g\in G}\operatorname{sort}\{m(gV):V\in\C\}.
\]
An independent Burnside computation verifies the orbit counts.  Selector
orbits over a canonical cover are computed as sections $R_U(\C)$ modulo
$K_\C$, which is equivalent to the global-left action after the cover has
been gauge-fixed.

\subsection{Complete enumeration}

\begin{theorem}[Cover and selector census]\label{thm:covers}
The $82$ atlas rows have $786$ unordered exact covers, forming $86$
global-left cover orbits.  Seventy-nine rows have one cover orbit.  The three
exceptions are
\[
\begin{array}{c|ccc}
\text{mask suffix}&\rowid{M00007D}&\rowid{M00016D}&\rowid{M001345}\\ \hline
\#\text{ cover orbits}&2&3&2.
\end{array}
\]
The $1{,}148$ multiplier selectors form $102$ global-left selector orbits.
Exactly $90$ of those orbits admit a representative that is a subgroup or a
one-sided subgroup coset; $2$ further orbits admit a genuine double-coset
representative but no subgroup/coset representative; the remaining $10$ are
residual.
\end{theorem}

\begin{table}[ht]
\centering
\caption{Cover and selector counts by tile size.}
\label{tab:cover-by-k}
\begin{tabular}{@{}rrrrr@{}}
\toprule
$|U|$ & tile rows & raw covers & cover orbits & selector orbits\\
\midrule
$6$  & $14$ & $102$ & $18$ & $24$\\
$8$  & $18$ & $144$ & $18$ & $21$\\
$12$ & $50$ & $540$ & $50$ & $57$\\
\midrule
total & $82$ & $786$ & $86$ & $102$\\
\bottomrule
\end{tabular}
\end{table}

\begin{proof}[Proof of \cref{thm:covers}]
For each row, the recursive and combination enumerators return the same
sorted cover stream.  Global-left canonicalisation produces the stated
orbit counts, and Burnside's lemma gives the same result independently.
For every cover representative, all selector sections are generated by the
right-$H_U$ fibres and quotiented by $K_\C$.  The subgroup inventory of
$S_4$ is regenerated from closure and contains exactly $30$ subgroups.
Testing every selector orbit against that inventory and against all typed
one- and two-sided cosets yields the disjoint taxonomy $90+2+10=102$.
Every equality is set equality in the $24$-element group; no heuristic
isomorphism test enters the count.
\end{proof}

The phrase ``$90$ coset selectors'' would be too strong.  The theorem says
that $90$ \emph{orbits admit} a subgroup/coset representative; other
selectors in the same orbit need not themselves be presented in that form.

\subsection{The carrier double coset}

\begin{theorem}[Typed carrier structure]\label{thm:carrier}
For every canonical cover orbit, the selector-independent carrier is one
typed double coset:
\[
 B_\C=K_\C aH_U
\]
for a suitable $a\in G$.  Exactly $85$ of the $86$ carrier orbits admit a
subgroup/coset global-left gauge.  The cover attached to
\rowid{M0030CF} is the unique carrier-level genuine non-coset exception.
\end{theorem}
\begin{proof}
For a fixed piece $aU\in\C$, transitivity of $K_\C$ on the pieces of $\C$
gives $B_\C=K_\C aH_U$.  Direct enumeration verifies this equality and the
piece transitivity for all $86$ cover representatives.  The subgroup/coset
gauge test is then applied to the carriers themselves, separately from the
selector taxonomy, and has the unique stated exception.
\end{proof}

Three normalisers occur in the certificate and must not be conflated:
$N_G(H_U)$ for the tile stabiliser, $N_G(K_\C)$ for the cover stabiliser, and
$N_G(L_A)$ for the left stabiliser $L_A=\{g:gA=A\}$ of a selector.  A group
element lying in one of these normalisers is not automatically a symmetry of
the other typed object.
