\section{Rank-coloured contact complexes}\label{sec:contacts}

\subsection{Exact intersection data}

Every barycentric vertex $b_I$ has rank $|I|\in\{1,2,3,4\}$.  A chamber is
the simplex on one maximal flag of nonempty subsets of $\{0,1,2,3\}$.  For a
piece $U$, let $\mathcal B(U)$ be the closed rank-coloured simplicial
subcomplex formed by all faces of its chambers.  If $X,Y$ are two pieces in
one exact cover, define their contact complex by
\[
 \Om(X,Y)=\mathcal B(X)\cap\mathcal B(Y).
\]
Because chamber interiors are disjoint, this lies in the boundary shadow.
The coned complex retains the universal rank-$4$ barycentre when present.

For $S\subseteq\{1,2,3,4\}$, let $f_S(\Om)$ count faces whose vertex-rank set
is exactly $S$.  The full coloured flag vector has $15$ coordinates.  We use
the smaller proper-rank marginal
\[
 \kk(\Om)=\bigl(f_{\{1\}}(\Om),f_{\{2\}}(\Om),f_{\{3\}}(\Om)\bigr).
\]
It is important that $\kk$ is neither the ordinary $f$-vector nor the full
coloured flag vector.  Balanced complexes and flag enumeration provide the
classical background \cite{Stanley1979,Frohmader2012,White2022}.

Two exact contact complexes have the same \emph{$S_4$ type} when one
simultaneous rank-preserving relabelling of the four tetrahedral vertices
maps one labelled complex onto the other.  This is a geometric orbit notion,
not unrestricted abstract simplicial isomorphism.

\subsection{Selected-cover panel}

\begin{theorem}[Selected contact atlas]\label{thm:selected-contacts}
Choose the certified canonical cover for each of the $82$ tile rows.  The
resulting covers contain $188$ unordered within-cover piece pairs:
\[
84\text{ for }|U|=6,\qquad54\text{ for }|U|=8,\qquad
50\text{ for }|U|=12.
\]
Their contact complexes have $28$ distinct $\kk$ profiles and $84$ exact
simultaneous-$S_4$ types.  Exactly $11$ $\kk$ profiles contain more than one
exact type.
\end{theorem}
\begin{proof}
The barycentric faces are represented by exact ranked subset flags.  For each
pair, intersection is performed before any marginal is taken.  Acting by all
$24$ simultaneous label permutations and selecting the least encoded complex
gives the exact type.  Equality grouping of the $188$ records produces the
stated counts.  Recomputing $\kk$ from each full flag vector verifies the
proper-rank convention on every record.
\end{proof}

One collision illustrates the information loss.  For a particular
$\kk=(2,1,2)$ profile with ordinary face data $(6,9,4,0)$, the records split
into three different $15$-coordinate coloured flag vectors, with
multiplicities $4,18,4$.  The marginal sees identical numbers of vertices of
each proper rank but forgets how those ranks are incident.

\subsection{All covers and a local-to-global obstruction}

Now choose one canonical representative of each of the $86$ global-left
cover orbits.  Its complete graph on pieces has one edge per unordered piece
pair, labelled by the exact contact type.  The $86$ panels contain $212$
edges and have $82$ edgewise signature classes.

Let $E(\C)$ denote the unordered piece pairs of a cover.  For two covers of
the same tile size, \emph{edgewise equivalence} means
\[
 \exists\pi\ \forall e\in E(\C)\ \exists g_e\in S_4:
 \Om'_{\pi(e)}=g_e\Om_e,
 \tag{E}
\]
where $\pi$ is induced by one global permutation of the pieces.  A
\emph{global alignment} requires
\[
 \exists\pi\ \exists g\in S_4\ \forall e\in E(\C):
 \Om'_{\pi(e)}=g\Om_e.
 \tag{G}
\]
The same piece permutation occurs in both definitions.  Only the order of
the geometric quantifiers changes.

\begin{theorem}[Contact local-to-global obstruction]
\label{thm:contact-obstruction}
There are five unordered pairs of distinct cover-orbit representatives that
belong to the same tile row.  Exactly two of these pairs satisfy \textup{(E)}:
the pairs over \rowid{M00007D} and \rowid{M001345}.  None of the five
satisfies \textup{(G)}.  Consequently edgewise contact equivalence does not
imply one global tetrahedral alignment on the certified carrier.
\end{theorem}
\begin{proof}
The three multi-cover rows have respectively $2,3,2$ cover orbits, hence
$\binom22+\binom32+\binom22=5$ pairs.  For each pair, the replay enumerates
all piece permutations.  For \textup{(E)} it then tests membership in the
simultaneous-$S_4$ orbit edge by edge.  For \textup{(G)} it tests each of the
$24$ common group elements against every edge.  Two pairs pass the first
test and all five fail the second.  The global test examines $576$ cases per
pair and $2{,}880$ cases in total.
\end{proof}

The theorem is static.  It asserts no hinge motion, collision-free path,
continuous deformation, or mechanical realisability.
