\section{Ambient congruence, handedness, and transitivity}
\label{sec:ambient}

\subsection{A subdivision-insensitive corner locus}

The boundary triangulation of $|U|_T$ contains vertices introduced only by
subdivision of a planar face or a straight edge.  To obtain a geometric
screen independent of those artefacts, define $C_3(U)$ to be the set of
boundary points at which the span of the incident local boundary-plane
normals has rank three.  Coplanar subdivision does not change this locus.

\begin{lemma}[Completeness of the mesh-vertex corner screen]
\label[lemma]{lem:corner-strata}
For every chamber union $U$, each point of $C_3(U)$ is a vertex of the
barycentric boundary mesh.  Equivalently, computing the normal rank at all
boundary mesh vertices finds the complete rank-three locus, whether or not
the polyhedral boundary is manifold along every mesh edge.
\end{lemma}
\begin{proof}
At the relative interior of a boundary triangle there is one local boundary
plane, so the normal rank is one.  At the relative interior of a mesh edge
$e$, every incident boundary plane contains the direction of $e$.  All its
normals therefore lie in the two-dimensional subspace perpendicular to that
direction inside the three-dimensional affine space $H$, so their rank is at
most two.  This argument does not use manifold edge incidence.  Every
remaining boundary stratum is a mesh vertex.
\end{proof}

\begin{lemma}[Corner-locus covariance]\label[lemma]{lem:corner-covariance}
If an affine Euclidean isometry $F:H\to H$ maps $|U|_T$ onto $|V|_T$, then
$F(C_3(U))=C_3(V)$.  If $C_3(U)$ affinely spans $H$, an isometry is uniquely
determined by the images of any affine basis of four locus points.
\end{lemma}
\begin{proof}
An isometry maps boundary planes to boundary planes and preserves the rank of
their normal span, proving covariance.  An affine map on a three-dimensional
affine space is determined by four affinely independent points.  The
isometry condition is then an exact equality of Gram matrices.
\end{proof}

\subsection{Global rigidity on the eligible carrier}

Let
\[
 \mathcal E=\{U\subseteq S_4:U\ne\varnothing,\quad
 \Gamma[U]\text{ is connected},\ |U|\mid24\}.
\]
The divisibility condition loses no possible congruent cover, because all
chambers have the same volume.  The exhaustive reduction of
\cref{tab:reduction} gives $|\mathcal E/S_4|=2{,}874$.  The global gate
constructs $C_3(U)$ for every one of these representatives before making any
exact-cover decision.  Its load-bearing counts are shown in
\cref{tab:global-rigidity}.

\begin{table}[ht]
\centering
\caption{Exact all-candidate congruence audit.  Pair counts include the
diagonal.  Class maps are enumerated on canonical $S_4$ corner classes;
all-candidate maps are obtained from them by the recorded transporters.}
\label{tab:global-rigidity}
\begin{tabular}{@{}lr@{}}
\toprule
audit stage & count\\
\midrule
eligible canonical candidates & $2{,}874$\\
all unordered candidate pairs & $4{,}131{,}375$\\
rejected by unequal volume & $568{,}587$\\
rejected by exact corner-distance signature & $3{,}460{,}040$\\
candidate pairs surviving both screens & $102{,}748$\\
canonical $S_4$ corner classes & $274$\\
canonical class pairs exhausted by both exact lanes & $290$\\
exact maps on canonical classes & $617$\\
maps derived on all candidate pairs & $228{,}599$\\
cross-class isometric pairs / non-$S_4$ maps / lane disagreements & $0/0/0$\\
\bottomrule
\end{tabular}
\end{table}

\begin{theorem}[Eligible-carrier congruence rigidity]
\label{thm:global-rigidity}
For $U,V\in\mathcal E$, the polyhedra $|U|_T$ and $|V|_T$ are freely
Euclidean congruent if and only if $V=gU$ for some $g\in S_4$.
\end{theorem}
\begin{proof}
The reverse implication follows from the coordinate isometry $\Phi_g$.
Suppose an isometry $F:H\to H$ maps $|U|_T$ onto $|V|_T$.  By
\cref{lem:corner-covariance}, it maps $C_3(U)$ isometrically onto $C_3(V)$.
The exact audit finds affine rank three for all $2{,}874$ canonical candidate
loci.  By \cref{lem:corner-strata}, this is the complete rank-three locus:
the $1{,}809$ candidates with nonmanifold mesh-edge incidence require no
extra hypothesis, and the independent edge-stratum audit finds zero
rank-three nonvertex strata.

Coordinate canonicalisation reduces the candidate loci to $274$ exact
$S_4$ classes.  Any isometry of two original loci conjugates, by their
recorded coordinate transporters, to a map between canonical classes.
Exact distance signatures leave the $290$ class pairs in
\cref{tab:global-rigidity}.  Weighted distance-graph backtracking and
affine-basis Gram reconstruction independently exhaust those pairs and agree
on all $617$ class-level maps.  No two distinct canonical classes are
isometric, and every enumerated map is induced by one coordinate permutation
$\Phi_g$.  The underlying covariance is checked once at the primitive level:
$24$ chamber bijections, $576$ chamber tetrahedra, $2{,}304$ chamber facets,
$109{,}440$ facet-incidence comparisons, and $2{,}304$ normal lines imply all
$2{,}874\cdot24=68{,}976$ candidate-action cases.

Consequently $F$ and some $\Phi_g$ agree on $C_3(U)$.  Since that locus
affinely spans $H$, \cref{lem:corner-covariance} gives $F=\Phi_g$ on all of
$H$.  Hence $|V|_T=F(|U|_T)=\Phi_g(|U|_T)=|gU|_T$.  The closed Coxeter
chambers have pairwise disjoint relative interiors, so their union encoding
is injective; therefore $V=gU$.
\end{proof}

\begin{corollary}[Complete congruent Coxeter-pure atlas]
\label[corollary]{cor:congruent-atlas}
A connected Coxeter-pure piece covers $T$ by congruent Coxeter-pure copies if
and only if it has an exact left-translate cover.  Up to free congruence,
there are exactly $97$ such pieces: $15$ convex and $82$ nonconvex.  The
nonconvex classes have sizes $6,8,12$ with multiplicities $14,18,50$.
Thus the nonconvex Coxeter-pure problem of \cite{BabanskyyT2} is resolved
within the fixed chamber carrier of \cref{sec:model}.
\end{corollary}
\begin{proof}
In a congruent Coxeter-pure cover, equal volume forces the common chamber
count to divide $24$, so every member belongs to $\mathcal E$.  Fixing one
member $U$, \cref{thm:global-rigidity} writes every other member as $gU$.
Interior disjointness and union $T$ then give an exact left-translate cover.
The converse uses the coordinate isometries $\Phi_g$.  The counts and the
convexity split are \cref{thm:left-atlas}.
\end{proof}

\subsection{Tile congruence and chirality}

For every atlas row, $C_3(U)$ spans $H$.  We enumerate its complete weighted
distance-graph isomorphisms in two independent ways: backtracking on exact
distance profiles and affine-basis Gram reconstruction.  Each candidate map
is converted, when possible, to the unique coordinate permutation $\Phi_g$
and filtered by exact chamber-mask equality.  A corner-set symmetry is only
a candidate; it need not preserve the full piece.

\begin{theorem}[Ambient tile classification]\label{thm:tile-congruence}
The $82$ atlas rows are $82$ distinct free Euclidean congruence classes.
They split into $159$ classes under orientation-preserving congruence.  Of
the full classes, $77$ are chiral and $5$ achiral, so
\[
 159=2\cdot77+5.
\]
For every row, the full Euclidean self-isometry group equals the left tile
stabiliser $H_U$.
\end{theorem}
\begin{proof}
There are $3{,}321$ unordered cross-row pairs and $82$ diagonal pairs.  Exact
distance signatures reject $3{,}253$ cross pairs; the two independent
isometry algorithms examine the remaining $68$.  Across all $3{,}403$ pairs
including the diagonal, they produce $539$ candidate corner maps.  Every
candidate is induced by a coordinate permutation.  The mask filter leaves no
cross-row shape congruence and identifies every self-isometry with $H_U$.
Restricting the coordinate permutations to $A_4$ yields the oriented split
and the stated chirality count.
\end{proof}

This is the finer rowwise statement on the selected nonconvex atlas.
\Cref{thm:global-rigidity} supplies the logically prior all-candidate
completeness; the exact mask filter here identifies self-isometry groups and
the orientation-preserving split.

\subsection{Whole partitions}

For a cover $\C$, the union of its pieces is the entire tetrahedron $T$.
Any congruence between two whole partitions therefore maps $T$ onto itself,
permutes its four extreme vertices, and belongs to the coordinate $S_4$.
Unlike the tile argument, this reduction requires no corner-locus screen.

\begin{theorem}[Partition congruence and finite-container transitivity]
\label{thm:partition-congruence}
The $86$ global-left cover orbits are exactly $86$ full Euclidean congruence
classes of whole partitions.  They split into $151$ orientation-preserving
classes, with $65$ chiral and $21$ achiral full classes.

Every one of the $86$ partitions is tile-transitive under its full container
symmetry group $K_\C$.  Exactly $69$ are tile-transitive under the even
subgroup $K_\C\cap A_4$.  In the remaining $17$ cases the cover stabiliser
has type $C_4$, and an orientation-reversing symmetry is necessary for piece
transitivity.
\end{theorem}
\begin{proof}
An isometry of a whole partition preserves its union $T$ and is therefore a
coordinate permutation.  Exact cover canonicalisation has already quotiented
this full $S_4$ action, proving the first count.  Restriction to $A_4$ gives
the $151=2\cdot65+21$ oriented classes.  Direct orbit computation of $K_\C$
on the pieces gives one orbit in all $86$ cases; repeating with the even
subgroup gives one orbit in $69$.  The stabiliser inventory identifies all
$17$ failures as type $C_4$.
\end{proof}

The term \emph{finite-container tile-transitive} is used to prevent a common
overreading.  These are partitions of one tetrahedron; the theorem does not
construct or classify periodic tilings of $\mathbb R^3$.  Moreover, an odd
tetrahedral isometry need not be reflection in a plane.
