%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Nonconvex A3 Coxeter-Chamber Atlas
%% Public companion manuscript and exact reproducibility package.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper]{amsart}
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage[protrusion=true,expansion=false]{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,enumitem,longtable,graphicx}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,capitalise,noabbrev]{cleveref}
\setlength{\emergencystretch}{3em}
\raggedbottom
\Urlmuskip=0mu plus 2mu\relax

\input{macros}

\hypersetup{
  pdftitle={The Nonconvex A3 Coxeter-Chamber Atlas: Congruence Rigidity, Exact Covers, and Patterson Separation},
  pdfauthor={Oleksiy Babanskyy},
  pdfsubject={congruence rigidity and finite classification of nonconvex Coxeter-pure tetrahedral tilings},
  pdfkeywords={Coxeter complex, regular tetrahedron, exact cover, symmetric group, Patterson function, homometry, congruent dissection}
}

\title[The nonconvex $A_3$ chamber atlas]
{The Nonconvex $A_3$ Coxeter-Chamber Atlas:\\
Congruence Rigidity, Exact Covers, and Patterson Separation}
\author{Oleksiy Babanskyy}
\date{}

\begin{document}
\begin{abstract}
\input{sections/00_abstract}
\end{abstract}
\maketitle

\noindent\textbf{Keywords.}
Coxeter complex; regular tetrahedron; congruent dissection; exact cover;
symmetric group; Patterson function; homometry; coloured flag complex.

\smallskip
\noindent\textbf{MSC 2020.}
Primary: 52C20, 05B45. Secondary: 20B30, 05E18, 52B15.

\tableofcontents

\input{sections/01_introduction}
\input{sections/02_model_and_equivalences}
\input{sections/03_finite_reduction_and_atlas}
\input{sections/04_patterson_separation}
\input{sections/05_covers_and_selectors}
\input{sections/06_contact_atlas}
\input{sections/07_ambient_symmetry}
\input{sections/08_boundary_presentations}
\input{sections/09_prior_art_and_scope}
\input{sections/10_reproducibility}

\appendix
\input{appendices/A_search_completeness}
\input{appendices/B_atlas_catalogue}
\input{appendices/C_certificate_crosswalk}

\section*{Data and code availability}
The public companion repository at
\url{https://github.com/aconsciousfractal/FCIG-Nonconvex-Coxeter-Pure-Atlas}
contains the complete machine-readable atlas, exact standard-library replay
code, generated tables, pinned JSON certificates, and a SHA-256 manifest.
The package is designed to run without network access or a neighbouring
checkout.  No archival DOI has yet been assigned.

\bibliographystyle{alpha}
\bibliography{refs}
\end{document}
